THE HYDROGEN EPOCH OF REIONIZATION ARRAY DISH: CHARACTERIZATION OF THE INSTRUMENTAL RESPONSE WITH REFLECTOMETRY MEASUREMENTS AND ITS IMPLICATIONS ON THE MEASUREMENT OF 21CM POWER SPECTRUM.

### 2016-02-25 DishReflectometry/Paper1_v1.tex
Changed equation 3

Since it was first proposed in ~\citep{Shaver_et_al1999} measuring 21~cm
emission from neutral hydrogen in our early universe has gained attention as a
powerful probe of both cosmology and astrophysics.  While the science case for
21~cm cosmology, particularly during the Epoch of Reionization, is well
established (see, e.g.,
~\citep{furlanetto_et_al2006,morales_wyithe2010,pritchard_loeb2012}),
the technical path toward measuring this signal has been extremely challenging.  The
weakness of this hyperfine line keeps the 21~cm signal below opacity throughout
cosmological history, but it also creates sensitivity and calibration
challenges that are yet to be fully solved.  With noise temperatures dominated
by sky noise ~\citep{XXX} and foregrounds four to five orders of magnitude
brighter than the signal ~\citep{XXX}, 
sky-averaged 21~cm monopole experiments such as
(EDGES; ~\citealt{XXX}),
(BIGHORNS; ~\citealt{XXX}),
(SARAS; ~\citealt{patra_et_al2014}),
(SCIHI; ~\citealt{voytek_et_al2014}),
(HYPERION; ~\citealt{presley_et_al2015})
% XXX others?
and 21~cm reionization power spectrum experiments such as
the LOw Frequency ARray (LOFAR; ~\citealt{XXX}),
the Murchison Widefield Array (MWA; ~\citealt{XXX}),
the Giant Metre-wave Radio Telescop (GMRT; ~\citealt{XXX}),
the Donald C. Backer Precision Array to Probe the Epoch of Reionization (PAPER; ~\citealt{parsons_et_al2010}),
the Hydrogen Epoch of Reionization Array (HERA; ~\citealt{XXX}),
and the future Square Kilometre Array (SKA; ~\citealt{XXX})
must
furnish both collecting area and foreground suppression at levels significantly
beyond anything previously achieved in radio telescopes operating below 1 GHz.

@@

%i.e, the complex visibility is the Fourier transform of the product of the antenna beam pattern with the sky angular power spectrum. In other words, it is the convolution of the Fourier transform of the antenna power pattern with the Fourier transform of the sky. The complex visibility measured by an interferometer with a given baseline length has explicit dependence on frequency as well as implicit frequency dependence through the spatial frequency $\vec u = \nu { \vec b \over c}$ component. Since $\vec u $ is the For a given baseline length $|\vec b|$, the visibility measured at various frequencies are not only the function of frequencies but also samples different $\vec u$ in the uv space. Delay transformation technique takes the visibility measurements at different frequencies and Fourier transforms the complex visibilities. If we defineI_{sky} the Fourier conjugate of the frequency axis as $\tau$ then the equation could be written as, 
In ~\citet{parsons_et_al2012a}, the Fourier transform of the visibility along the frequency axis was introduced,
resulting in the delay spctrum:
\begin{eqnarray}
\tilde V(\vec b, \tau) & = & \int\!\!\int{\beam(\thhat,\nu) I_\sky(\thhat,\nu) \ifngexp d\Omega~e^{+2\pi i\nu\tau}d\nu}\nonumber\\	                        & = &   \int \left [ A(\thhat, \tau)\ast I_{sky}(\thhat, \tau) \ast \delta( \tau - \frac{{\vec {b} \cdot \thhat}}{c} )\right ] d\Omega 
\label{eq3}
\end{eqnarray}
% XXX rethink how to express this equation (not correct about integrated over all sky)
% XXX define tau_g
The convolution is carried out along the $\tau$ axis which is Fourier conjugate of the frequency $\nu$. In words, the sky delay spectrum from any direction $\thhat$ is convoluted with the delay spectrum of the instrument and would be located at the delay $\tau = {\vec b \cdot \thhat \over c}$ %defined this differently earlier
 in the delay domain. The maximum geometric delay possible for a given base line would be $\tau_{g} ={ b \over c }$ for the direction of $\thhat = 0$ when the phase centre is halfway in between the two antennas. %The phase center is elsewhere defined as being at the center of one of the antennas.
 Hence, the sky contribution from any direction would be confined within $-\tau_{g}<\tau<\tau_{g}$. Due to chromaticity of the sky signal as well as instrument reponse, the delay spectrum of the sky spills over the delay $\tau> \tau_{g}$ with decaying amplitude [Ref to the figure Parsons12]. Sky delay spectrum $I_{sky}(\tau)$ is contributed by the foreground  $I_{fg}(\tau)$  which is spectrally smooth and the 21~cm power spectrum $I_{21}(\tau)$ which contains spectral signatures. Therefore, in the spill over region $(\tau>\tau_{g})$, the relative strength of the smooth spectrum foreground with respect to the delay spectrum of the $I_{21}$ reduces and the 21~cm delay spectrum could potentially be detectable.

@@

%\subsection{Visibility and delay spectrum computation considering multiple reflections}
Upon first incidence of the sky signal $\volt_{sky}$, $\Gamma_{f}$ fraction of the voltage is reflected off the feed while $(1-\Gamma_{f})$ fraction is coupled to the feed. The reflected voltage then further reflected off the dish and $(1-\Gamma_{f}) $ fraction of it reenters the feed with a roundtrip time delay $\Delta \tau$. Hence, if $I_{sky}$ is reflected n times in between the feed and the dish, the net voltage entering the feed after an
$n^{th}$ reflection off the feed and the dish is written as:
\begin{eqnarray}
\volt_{1} & = &  \bmvolt (1-\Gamma_{f}) \volt_{sky}[1+ \Gamma_{f}\Gamma_{d} \dfngexp \nonumber \\
	&& + (\Gamma_{f}\Gamma_{d})^2  (\dfngexp)^{2}+ \nonumber \\
&&  ....+ (\Gamma_{f}\Gamma_{d})^{n} (\dfngexp)^{n}] \nonumber
\end{eqnarray}
and, 
\begin{eqnarray}
\volt_{2} & = &  \bmvolt (1-\Gamma_{f}) \volt_{sky}[1+ \Gamma_{f}\Gamma_{d} \dfngexp \nonumber\\
&&+  (\Gamma_{f}\Gamma_{d})^2  (\dfngexp)^{2}+ \nonumber \\
&& ....+ (\Gamma_{f}\Gamma_{d})^{n} (\dfngexp)^{n}] \ast \fngexp \nonumber
\end{eqnarray}
Frequency as well as angular dependence of the quantities are not written explicitly for notational simplicity. We also absorb the common gain term $(1-\Gamma_{f})$ with antenna field pattern $a$ and denote them as $\bmvolt_{f}= \bmvolt(1-\Gamma_{f})$ here after. The cross power generated by $v_{1}$ and $v_{2}$ would have spurious visibility response due to mutual correlation between multiply reflected voltages. Fourier transform of this visibility spectrum along the frequency axis results in the delay spectrum. 
In the delay domain, visibility contributed by any two voltage components from two antennas with no mutual delay will be located at the delay $\tau = 0$ whereas any two voltage components from two antennas components having a mutual delay of $n\Delta \tau$ will be centred at $n\Delta \tau$. These will broaden the width of the delay spectrum which finally interferes with the 21cm power spectrum detection. Combining these terms, the expression of visibility will be,

\begin{eqnarray}\label{eqn:series1}
\vis(\vec b, \nu) & = & \int \volt_{1}\volt_{2}^{*} d\Omega \nonumber\\
			& = & \int I_{sky}(\vec b, \nu)\Sigma(\vec b, \nu) \fngexp d\Omega
\end{eqnarray}

where we define a combined common instrument parameter, written as, 
 \begin{eqnarray}
\Sigma(\vec b, \nu) & = & \beam_{f}  [ 1+  \Gamma_{f}\Gamma_{d} \dfngexp \nonumber\\
&& + (\Gamma_{f}\Gamma_{d})^2(\dfngexp)^{2}+ \nonumber\\
&&  ....+(\Gamma_{f}\Gamma_{d})^{n}(\dfngexp)^{n}  ]\\
& = & \beam_{f}\displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}\dfngexp]^{n}
   \nonumber\\
   \label{eq6}
\end{eqnarray}
where, $\beam_{f}=\bmvolt_{f}\bmvolt_{f}^{*}$ is the antenna cross power pattern.
and the delay spectrum would be, 
\begin{eqnarray}
%\tilde V(\vec b, \tau) & = & \int \left [ \int I_{sky}(\vec b, \nu)\Sigma(\vec b, \nu) \fngexp  d\Omega \right ]  e^{-2\pi i\nu\tau} d\nu \nonumber \\
\tilde V(\vec b, \tau) & = & \int \left [ I_{sky}(\thhat, \nu) \ast \Sigma(\thhat, \nu) \ast \delta( \tau - \frac{{\vec {b} \cdot \thhat}}{c} )  \right] d\Omega
\label{eq7}
\end{eqnarray}

 Thus, the correlation between the reflected signal  from the feed and subsequently from the dish with the direct signal extends the foreground response to delays beyond the maximum geometric delay for a given baseline and contaminates the delay mode where 21~cm delay spectrum could potentially be detected. \\
The design specification of HERA elements requires that any
signal, arriving at the feed at a delay $\Delta \tau$ with respect to the direct incidence, should be
at the level of $-60dB$ at a delay of $60ns$ relative to the first incident
signal at the feed ~\citep{parsons_deboer_memo}. This specification was
approximated based on the power level of the cosmological signal in relation to
foreground signals, which is estimated to be six orders of magnitude fainter ~\citep{santos_et_al2005,ali_et_al2008,deoliveira2008,jelic_et_al2008,bernardi_et_al2009,bernardi_et_al2010,ghosh_et_al2011}. Additionally, the $14m$ HERA baselines set a foreground containing
horizon-limit (the wedge) that, with some buffer, sets a delay specification of
$60ns$
~\citep{parsons_et_al2012b,vedantham_et_al2012,nithya_et_al2013,liu_et_al2014a,liu_et_al2014b}. Our goal is to measure the instrument response $\Sigma(\nu)$ and its effect on the power spectrum measurements. 
%++++++++++++++++++++++++++++++++++++++++++++++++++++++
\section{Reflectometry measurements}
\begin{figure*}
\centering
\includegraphics[trim={2cm 10cm 20cm 5cm},clip, totalheight=0.3\textheight]{plots/herafeed.jpg}
\vspace{1.0 em}
\caption{HERA feed consists of a pair of crossed dipole ove xxx mt diameter backplane made of wire mesh. The backplane is surrounded by xxx m wire mesh around the edge resulting in encasing the cross dipole in a cylindrical cage.}
\label{fig:herafeed}
\end{figure*}
We carried out reflectometry measurements at the HERA element prototype in Green
Bank, WV (Figure \ref{fig:heradish}) in order to measure the instrument response of the feed and dish assembly and characterise its performance. An HERA element consists off a $14\,m$ diameter
parabolic reflector and a crossed-dipole pair as a feed. The cross dipole antenna pair is identical to the feed of the PAPER antenna which is suspended at the focal plane of the dish with the support of three vertical poles. HERA elements are closely spaced with centre to centre distance between two dishes are equal to the dish diameter. Therefore, to reduce the coupling between the adjacent dishes, the crossed dipole feed along with the back plane is encased in a cylindrical cage. The feed is raised and
lowered by a three-pulley system mounted on the three poles. The focal height of the dish is $5m$.  
As given in the previous section, if the incident power from the sky signal is $I_{sky}$, the feed
reflection coefficient is $\Gamma_{f}$, and the dish reflection
coefficient is $\Gamma_{d}$, then the net power entering a feed after
$n^{th}$ reflection off the feed and the dish is:

@@

\begin{eqnarray}\label{eqn:ratio1}
{I_{meas} \over I_{sky} } & = & \Sigma(\vec b, \nu) \nonumber\\
  & = & \beam_{f} \displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}\dfngexp]^{n}
   \nonumber\\
   \label{eq8}
\end{eqnarray}

@@

The total reflected power, returned to the VNA, denoted by $I_{ret}$ would be:
\begin{eqnarray}\label{eqn:series2}
I_{ret} & = & \Gamma_{f}I_{tr}+ I_{r}(1-\Gamma_{f}) [\Gamma_{d} \dfngexp + \Gamma_{f}\Gamma_{d}^{2} (\dfngexp)^{2}\nonumber\\
&&+ ....+ \Gamma_{f}^{n-1}\Gamma_{d})^{n}(\dfngexp)^{n}]
\end{eqnarray}

@@

  \begin{eqnarray}\label{eqn:ratio2}
 {I_{ret} \over I_{tr} } & = & \Gamma_{f}
  +  \Gamma_{d}(1-\Gamma_f) \beam_{f} I_{tr} [e^{i\phi}+ \Gamma_{f}\Gamma_{d} e^{i2\phi}\nonumber\\ 
  && +  ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{i n\phi}]\nonumber\\
  & = & \Gamma_{f} + { (1-\Gamma_f)\beam_{f}\over \Gamma_{f} } \displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}e^{i\phi}]^{n}
 \label{eq9}
\end{eqnarray}

The ratio in Equation \ref{eqn:ratio2} is identical to the ratio in the sky
observation in Equation \ref{eqn:ratio1} except in two factors. The
first factor corresponds to an additive amplitude difference arising from
$\Gamma_{f}$, which physically accounts for the initial reflection at the feed.
The second difference is the multiplicative ${ (1-\Gamma_f)\over \Gamma_{f} }$. Our measurement is corrected  for these two terms to map the instrument response measurements from transmission mode in which the measurement is taken to receiving mode in which the sky observation is done.

%++++++++++++++++++++++++++++++++++++++++++++++++++++++
\section{Results}
\begin{figure*}[ht]
\begin{minipage}[b]{0.5\linewidth}
\centering
\includegraphics[angle=0, width=\linewidth]{plots/s11_HERA_feed_PAPER_mag.png}
\end{minipage}
\hspace{0.1cm}
\begin{minipage}[b]{0.5\linewidth}
\centering
\includegraphics[angle=0, width=\linewidth]{plots/s11_HERA_feed_PAPER_ph.png}
\end{minipage}
\caption{Left: Magnitude of the return loss of power measured in between 100 to 200 MHz using vector network analyser. Right panel shows the corresponding phase.HERA feed design is derived from modified PAPER antenna and therefore the return loss closely relates to the PAPER antenna response with slight frequency shift. The return loss measured when the HERA feed is suspended over the dish is, however, show deviation from the feed performance. }
\label{fig:freq}       
\end{figure*}

>>>>

Since it was first proposed in ~\citep{Shaver_et_al1999} measuring 21~cm
emission from neutral hydrogen in our early universe has gained attention as a
powerful probe of both cosmology and astrophysics.  While the science case for
21~cm cosmology, particularly during the Epoch of Reionization, is well
established (see, e.g.,
~\citep{furlanetto_et_al2006,morales_wyithe2010,pritchard_loeb2012}),
the technical path toward measuring this signal has been extremely challenging.  The
weakness of this hyperfine line keeps the 21~cm signal below opacity throughout
cosmological history, but it also creates sensitivity and calibration
challenges that are yet to be fully solved.  With noise temperatures dominated
by sky noise ~\citep{XXX} and foregrounds four to five orders of magnitude
brighter than the signal ~\citep{XXX}, 
sky-averaged 21~cm monopole experiments such as
(EDGES; ~\citealt{XXX}),
(BIGHORNS; ~\citealt{XXX}),
(SARAS; ~\citealt{patra_et_al2014}),
(SCIHI; ~\citealt{voytek_et_al2014}),
(HYPERION; ~\citealt{presley_et_al2015})
% XXX others?
and 21~cm reionization power spectrum experiments such as
the LOw Frequency ARray (LOFAR; ~\citealt{XXX}),
the Murchison Widefield Array (MWA; ~\citealt{XXX}),
the Giant Metre-wave Radio Telescope (GMRT; ~\citealt{XXX}),
the Donald C. Backer Precision Array to Probe the Epoch of Reionization (PAPER; ~\citealt{parsons_et_al2010}),
the Hydrogen Epoch of Reionization Array (HERA; ~\citealt{XXX}),
and the future Square Kilometre Array (SKA; ~\citealt{XXX})
must
furnish both collecting area and foreground suppression at levels significantly
beyond anything previously achieved in radio telescopes operating below 1 GHz.

@@

%i.e, the complex visibility is the Fourier transform of the product of the antenna beam pattern with the sky angular power spectrum. In other words, it is the convolution of the Fourier transform of the antenna power pattern with the Fourier transform of the sky. The complex visibility measured by an interferometer with a given baseline length has explicit dependence on frequency as well as implicit frequency dependence through the spatial frequency $\vec u = \nu { \vec b \over c}$ component. Since $\vec u $ is the For a given baseline length $|\vec b|$, the visibility measured at various frequencies are not only the function of frequencies but also samples different $\vec u$ in the uv space. Delay transformation technique takes the visibility measurements at different frequencies and Fourier transforms the complex visibilities. If we defineI_{sky} the Fourier conjugate of the frequency axis as $\tau$ then the equation could be written as, 
In ~\citet{parsons_et_al2012a}, the Fourier transform of the visibility along the frequency axis was introduced,
resulting in the delay spctrum:
\begin{eqnarray}
\tilde V(\vec b, \tau) & = & \int\!\![{\beam(\vec b,\nu)*I_\sky(\vec b,\nu)] ~e^{-2\pi i\nu\tau}d\nu}\nonumber\\	                        %& = &   \left [ A(\vec b, \tau)\ast I_{sky}(\vec b, \tau) \ast \delta( \tau - \frac{{\vec {b} \cdot \thhat}}{c} )\right ] d\Omega 
\label{eq3}
\end{eqnarray}
% XXX rethink how to express this equation (not correct about integrated over all sky)
% XXX define tau_g
The convolution is carried out along the $\tau$ axis which is Fourier conjugate of the frequency $\nu$. In words, the sky delay spectrum from any direction $\thhat$ is convoluted with the delay spectrum of the instrument and would be located at the delay $\tau = {\vec b \cdot \thhat \over c}$ %defined this differently earlier
 in the delay domain. The maximum geometric delay possible for a given base line would be $\tau_{g} ={ b \over c }$ for the direction of $\thhat = 0$ when the phase centre is halfway in between the two antennas. %The phase center is elsewhere defined as being at the center of one of the antennas.
 Hence, the sky contribution from any direction would be confined within $-\tau_{g}<\tau<\tau_{g}$. Due to chromaticity of the sky signal as well as instrument reponse, the delay spectrum of the sky spills over the delay $\tau> \tau_{g}$ with decaying amplitude [Ref to the figure Parsons12]. Sky delay spectrum $I_{sky}(\tau)$ is contributed by the foreground  $I_{fg}(\tau)$  which is spectrally smooth and the 21~cm power spectrum $I_{21}(\tau)$ which contains spectral signatures. Therefore, in the spill over region $(\tau>\tau_{g})$, the relative strength of the smooth spectrum foreground with respect to the delay spectrum of the $I_{21}$ reduces and the 21~cm delay spectrum could potentially be detectable.
The convolution is carried out along the $\tau$ axis which is Fourier conjugate of the frequency $\nu$. In words, the sky delay spectrum from any direction $\thhat$ is convolved with the delay spectrum of the instrument and would be located at the delay $\tau = {\vec b \cdot \thhat \over c}$ in the delay domain. The maximum geometric delay possible for a given base line would be $\tau_{g} ={ b \over c }$ for the direction of $\thhat = 0$ when the phase centre is halfway in between the two antennas. Hence, the sky contribution from any direction would be confined within $-\tau_{g}<\tau<\tau_{g}$. Due to chromaticity of the sky signal as well as instrument reponse, the delay spectrum of the sky spills over the delay $\tau> \tau_{g}$ with decaying amplitude [Ref to the figure Parsons12]. Sky delay spectrum $I_{sky}(\tau)$ is contributed by the foreground  $I_{fg}(\tau)$  which is spectrally smooth and the 21~cm power spectrum $I_{21}(\tau)$ which contains spectral signatures. Therefore, in the spill over region $(\tau>\tau_{g})$, the relative strength of the smooth spectrum foreground with respect to the delay spectrum of the $I_{21}$ reduces and the 21~cm delay spectrum could potentially be detectable.

@@

%\subsection{Visibility and delay spectrum computation considering multiple reflections}
Upon first incidence of the sky signal $\volt_{sky}$, $\Gamma_{f}$ fraction of the voltage is reflected off the feed while $(1-\Gamma_{f})$ fraction is coupled to the feed. The reflected voltage then further reflected off the dish and $(1-\Gamma_{f}) $ fraction of it reenters the feed with a roundtrip time delay $\Delta \tau$. Hence, if $I_{sky}$ is reflected n times in between the feed and the dish, the net voltage entering the feed after an
$n^{th}$ reflection off the feed and the dish is written as:
\begin{eqnarray}
\volt_{1} & = &  \bmvolt (1-\Gamma_{f}) \volt_{sky}[1+ \Gamma_{f}\Gamma_{d} \dfngexp \nonumber \\
	&& + (\Gamma_{f}\Gamma_{d})^2  (\dfngexp)^{2}+ \nonumber \\
&&  ....+ (\Gamma_{f}\Gamma_{d})^{n} (\dfngexp)^{n}] \nonumber
\end{eqnarray}
and, 
\begin{eqnarray}
\volt_{2} & = &  \bmvolt (1-\Gamma_{f}) \volt_{sky}[1+ \Gamma_{f}\Gamma_{d} \dfngexp \nonumber\\
&&+  (\Gamma_{f}\Gamma_{d})^2  (\dfngexp)^{2}+ \nonumber \\
&& ....+ (\Gamma_{f}\Gamma_{d})^{n} (\dfngexp)^{n}] \fngexp \nonumber
\end{eqnarray}
Frequency as well as angular dependence of the quantities are not written explicitly for notational simplicity. We also absorb the common gain term $(1-\Gamma_{f})$ with antenna field pattern $a$ and denote them as $\bmvolt_{f}= \bmvolt(1-\Gamma_{f})$ here after. The cross power generated by $v_{1}$ and $v_{2}$ would have spurious visibility response due to mutual correlation between multiply reflected voltages. Fourier transform of this visibility spectrum along the frequency axis results in the delay spectrum. 
In the delay domain, visibility contributed by any two voltage components from two antennas with no mutual delay will be located at the delay $\tau = 0$ whereas any two voltage components from two antennas components having a mutual delay of $n\Delta \tau$ will be centred at $n\Delta \tau$. These will broaden the width of the delay spectrum which finally interferes with the 21cm power spectrum detection. Combining these terms, the expression of visibility will be,

\begin{eqnarray}\label{eqn:series1}
\vis(\vec b, \nu) & = & \int \volt_{1}\volt_{2}^{*} d\Omega \nonumber\\
			& = & \int I_{sky}(\vec b, \nu)\Sigma(\nu) \fngexp d\Omega
\end{eqnarray}

where we define a combined common instrument parameter, written as, 
 \begin{eqnarray}
\Sigma( \nu) & = & \beam_{f}  [ 1+  \Gamma_{f}\Gamma_{d} \dfngexp \nonumber\\
&& + (\Gamma_{f}\Gamma_{d})^2(\dfngexp)^{2}+ \nonumber\\
&&  ....+(\Gamma_{f}\Gamma_{d})^{n}(\dfngexp)^{n}  ]\\
& = & \beam_{f}+\beam_{f} \displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}\dfngexp]^{n}
   \nonumber\\ 
   \label{eq6}
\end{eqnarray}
where, $\beam_{f}=\bmvolt_{f}\bmvolt_{f}^{*}= |a(1-\Gamma_{f})|^{2}$ is the antenna cross power pattern.
and the delay spectrum would be, 
\begin{eqnarray}
%\tilde V(\vec b, \tau) & = & \int \left [ \int I_{sky}(\vec b, \nu)\Sigma(\vec b, \nu) \fngexp  d\Omega \right ]  e^{-2\pi i\nu\tau} d\nu \nonumber \\
\tilde V(\vec b, \tau) & = & \int \left [ I_{sky}(\thhat, \nu) \ast \Sigma(\thhat, \nu) \ast \delta( \tau - \frac{{\vec {b} \cdot \thhat}}{c} )  \right] d\Omega
\label{eq7}
\end{eqnarray}

 Thus, the correlation between the reflected signal  from the feed and subsequently from the dish with the direct signal extends the foreground response to delays beyond the maximum geometric delay for a given baseline and contaminates the delay mode where 21~cm delay spectrum could potentially be detected. \\
The design specification of HERA elements requires that any
signal, arriving at the feed at a delay $\Delta \tau$ with respect to the direct incidence, should be
at the level of $-60dB$ at a delay of $60ns$ relative to the first incident
signal at the feed ~\citep{parsons_deboer_memo}. This specification was
approximated based on the power level of the cosmological signal in relation to
foreground signals, which is estimated to be six orders of magnitude fainter
~\citep{santos_et_al2005,  ali_et_al2008,deoliveira2008, jelic_et_al2008, bernardi_et_al2009,bernardi_et_al2010, ghosh_et_al2011}. Additionally, the $14m$ HERA baselines set a foreground containing
Additionally, the $14m$ HERA baselines set a foreground containing
horizon-limit (the wedge) that, with some buffer, sets a delay specification of
$60ns$
~\citep{parsons_et_al2012b,vedantham_et_al2012,nithya_et_al2013,liu_et_al2014a,liu_et_al2014b}. Our goal is to measure the instrument response $\Sigma(\nu)$ and its effect on the power spectrum measurements. 
%++++++++++++++++++++++++++++++++++++++++++++++++++++++
\section{Reflectometry measurements}
\begin{figure*}
\centering
\includegraphics[trim={2cm 10cm 20cm 5cm},clip, totalheight=0.3\textheight]{plots/herafeed.jpg}
\vspace{1.0 em}
\caption{HERA feed consists of a pair of crossed dipole ove xxx mt diameter backplane made of wire mesh. The backplane is surrounded by xxx m wire mesh around the edge resulting in encasing the cross dipole in a cylindrical cage.}
\label{fig:herafeed}
\end{figure*}
We carried out reflectometry measurements at the HERA element prototype in Green
Bank, WV (Figure \ref{fig:heradish}) in order to measure the instrument response of the feed and dish assembly and characterise its performance. An HERA element consists off a $14\,m$ diameter
parabolic reflector and a crossed-dipole pair as a feed. The cross dipole antenna pair is identical to the feed of the PAPER antenna which is suspended at the focal plane of the dish with the support of three vertical poles. HERA elements are closely spaced with centre to centre distance between two dishes are equal to the dish diameter. Therefore, to reduce the coupling between the adjacent dishes, the crossed dipole feed along with the back plane is encased in a cylindrical cage. The feed is raised and
lowered by a three-pulley system mounted on the three poles. The focal height of the dish is $5m$.  
As given in the previous section, if the incident power from the sky signal is $I_{sky}$, the feed
reflection coefficient is $\Gamma_{f}$, and the dish reflection
coefficient is $\Gamma_{d}$, then the net power entering a feed after
$n^{th}$ reflection off the feed and the dish is:

@@

\begin{eqnarray}\label{eqn:ratio1}
{I_{meas} \over I_{sky} } & = & \Sigma(\vec b, \nu) \nonumber\\
  & = & \beam_{f}+ \beam_{f} \displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}\dfngexp]^{n}
   \nonumber\\
   \label{eq8}
\end{eqnarray}

@@

The total reflected power returned to the VNA, as measured by the VNA would be:
\begin{eqnarray}\label{eqn:series2}
I_{meas} & = & \Gamma_{f}I_{tr}+ I_{r}(1-\Gamma_{f}) [\Gamma_{d} \dfngexp + \Gamma_{f}\Gamma_{d}^{2} (\dfngexp)^{2}\nonumber\\
&&+ ....+ \Gamma_{f}^{n-1}\Gamma_{d})^{n}(\dfngexp)^{n}]
\end{eqnarray}

@@

  \begin{eqnarray}\label{eqn:ratio2}
 {I_{meas} \over I_{tr} } & = & \Gamma_{f}
  +  \Gamma_{d}(1-\Gamma_f) \beam_{f} I_{tr} [e^{i\phi}+ \Gamma_{f}\Gamma_{d} e^{i2\phi}\nonumber\\ 
  && +  ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{i n\phi}]\nonumber\\
  & = & \Gamma_{f} + { (1-\Gamma_f)\beam_{f}\over \Gamma_{f} } \displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}e^{i\phi}]^{n}
 \label{eq9}
\end{eqnarray}

The ratio in Equation \ref{eqn:ratio2} is identical to the ratio in the sky
observation in Equation \ref{eqn:ratio1} except in three factors. The
first factor corresponds to an additive amplitude difference arising from
$\Gamma_{f}$, which physically accounts for the initial reflection at the feed.
The second difference is the multiplicative ${ (1-\Gamma_f)\over \Gamma_{f} }$. In addition, in order to estimate the true response of the system to the sky signal in the receiving mode, we add the term $A_{f}$.  These corrections map the measured instrument response from transmission mode in which the measurement is taken to receiving mode in which the sky observation is done. The corrected measurement could be written as
 \begin{eqnarray}\label{eqn:ratio2}
 \left[{I_{meas} \over I_{tr}}-\Gamma_{f}\right]{ \Gamma_{f} \over (1-\Gamma_{f})} + \beam_{f}  & = & \beam_{f}+ \beam_{f} \displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}e^{i\phi}]^{n}\nonumber\\
 & = & {I_{meas} \over I_{sky} }
 \label{eq9}
\end{eqnarray}
%++++++++++++++++++++++++++++++++++++++++++++++++++++++
\section{Results}
\begin{figure*}[ht]
\begin{minipage}[b]{0.5\linewidth}
\centering
\includegraphics[angle=0, width=\linewidth]{plots/s11_HERA_feed_PAPER_mag.png}
\end{minipage}
\hspace{0.1cm}
\begin{minipage}[b]{0.5\linewidth}
\centering
\includegraphics[angle=0, width=\linewidth]{plots/s11_HERA_feed_PAPER_ph.png}
\end{minipage}
\caption{Left: Magnitude of the return loss of power measured in between 100 to 200 MHz using vector network analyser. Right panel shows the corresponding phase.HERA feed design is derived from modified PAPER antenna and therefore the return loss closely relates to the PAPER antenna response with slight frequency shift. The return loss measured when the HERA feed is suspended over the dish is, however, show deviation from the feed performance. }
\label{fig:freq}       
\end{figure*}
